\pagebreak
\section{A2 - Recollect}

% A2 Intel brief
\GTFOIntelBlock{Prisoners sent to locate and retrieve hisec crate.  %
Unknown ceiling dwelling biomass present.  %
Prisoners failing to exercise caution will not be considered a loss.}

% A2 interrupted communications
\GTFOIntCommsBlock{
\GTFOIntCommsLine{> ... Wasn't this room empty before?}
\GTFOIntCommsRedLine{> ... I told you those black cocoons were bad news...}
\GTFOIntCommsLine{> ... Fuck, I hate this place even more now.}
}

\GTFOPermitsBlock{
\GTFOPermitHigh
\GTFOPermitExtreme
\GTFOPermitOverload
\GTFOPermitPrisonerEfficiency}

\GTFOExpeditionMetricsBlock{
\item{\textbf{Drop cage target depth:} 498 meters}
}

% ==> Zone Connectivity Diagram
\pagebreak
\subsection{Zone Connectivity}
\zonelayout{
\node{\textbf{Zone 15}\\
BHK
Hub}
    child {
        node {Zone 16}
        child[concept color=\LayoutStyleHighSectorRandomOption] {node {\textbf{Zone 17}\\
        ¿CKC?}}
        child[concept color=\LayoutStyleHighSectorRandomOption] {node {\textbf{Zone 18}\\
        ¿CKC?}}
        child {
            node {Zone 19}
            child { node {\textbf{Zone 20}\\
            Cargo}}
            child[concept color=\LayoutStyleOverloadSector] {node {\textbf{Zone 302}\\
            HDD}}
        }
    }
    child[concept color=\LayoutStyleExtremeSector] {
        node{Zone 131}
        child { node {Zone 132\\
        BHK}}
    }
}

\pagebreak
\subsection{High}

The objective of \textbf{High} is to Locate the Hi-Sec Cargo and bring it to Zone 15 (Extract).

\subsection{Extreme}

The objective of \textbf{Extreme} is to find the given terminal (in Zone 131) to Reroute Power.
\begin{itemize}
    \item Starting Zone is \zone{131} and is connected to \zone{15}
    \item This will turn off the lights.
    \item You will need to find the \gtfobhkey{Zone 132} as well.
    \item There will be \textbf{two} \gtfoenemyscout{} in \zone{132}.
\end{itemize}

\subsection{Overload}

The objective of \textbf{Overload} is to find the Hard Drive (in Zone 302), which is protected by a \textbf{single Mother}.

\subsection{Prisoner Efficiency}

\begin{itemize}
    \item Use the Bulkhead Key to unlock the \textbf{Extreme Bulkhead Door - Zone 131}
    \item Run the \texttt{REROUTE\_POWER} command on the Terminal in Zone 131
    \item Get the Bulkhead Key from Zone 132
    \item Use the Bulkhead Key to unlock the \textbf{High Bulkhead Door - Zone 16}
    \item Find the \textbf{Color Key Card} in either \textbf{Zone 17} or \textbf{Zone 18}
    \item Use the Color Key Card to unlock Security Door for Zone 19
    \item Do the Security Door Alarm for Zone 20's door.
    \item Have three people ready to run into Zone 302 and deal with Mother, her children, and locating the HDD.
    \item Pick up the Hi-Sec Cargo, and waddle towards the bridge that leads back to Extract.
    \item Drop the Hi-Sec Cargo on the Bridge and heal with Mother, the Children, and the HDD.
    \item Once you find the HDD (it'll be in a locker) head to extract
\end{itemize}
% END OF R5-A2
