\pagebreak
\section{B1 - Smother}

\GTFOIntelBlock{Specific DNS sample needed.  Prisoners sent to
retrieve HSU with matching tissue quality.\\
Air filtration system unstable.  Prisoners deemed expendable.}

\GTFOIntCommsBlock{
\GTFOIntCommsLine{>... Those horned monsters... They're - they're everywhere.}
\GTFOIntCommsRedLine{>... Hit them in the back, even better if they're sleeping.}
\GTFOIntCommsLine{>... [sudden noises]}
\GTFOIntCommsLine{>... Too late now! Aaargh!}
\GTFOIntCommsLine{>... [commotion, unintelligible]}
}

\GTFOPermitsBlock{
\GTFOPermitHigh
\GTFOPermitExtreme
\GTFOPermitOverload
\GTFOPermitPrisonerEfficiency
}

\GTFOExpeditionMetricsBlock{
\item Drop cage target depth: 702 meters
}

\pagebreak
\subsection{Zone Connectivity}
\zonelayout{
%\begin{tikzpicture}[mindmap, grow cyclic, every node/.style=concept, concept color=blue!30, 
%	level 1/.append style={level distance=5cm,sibling angle=90},
%	level 2/.append style={level distance=3cm,sibling angle=45},]
\node{Zone 92}
    child[concept color=\LayoutStyleHighSectorRandomOption] {node {Zone 93\\
    多CKC?}}
    child[concept color=\LayoutStyleHighSectorRandomOption] {node {Zone 97\\
    多CKC?}}
    child {
        node {Zone 94\\
        Hub}
        child {
            node {Zone 95}
            child[concept color=\LayoutStyleHighSectorRandomOption] {node {Zone 96\\
            多HSU?}}
            child[concept color=\LayoutStyleHighSectorRandomOption] {node {Zone 98\\
            多HSU?}}
            child {
                node {Zone 99\\
                BHK, Hub}
                child[concept color=\LayoutStyleOverloadSector] {
                    node {Zone 452}
                    child {
                        node {Zone 453}
                        child {
                            node {Zone 454}
                            child {node {Zone 455}}
                        }
                    }
                    child {node {Zone 456}}
                }
            }
        }
        child[concept color=\LayoutStyleExtremeSector] {
            node {Zone 223}
            child {node {Zone 224}}
            child {node {Zone 225}}
            child {node {Zone 226}}
        }
    }
}

\pagebreak
\paragraph{Ad-Hoc Notes}
\begin{itemize}
    \item This mission is the one with the large first room that has a lot of ladders and levels that are very maze-like.
    \item Zone 92A is where this mission begins.
\end{itemize}

\paragraph{ZONE\_092 - The first big room}
\begin{itemize}
    \item {\color{Blue}Passage to Zone 93, Zone 94, and Zone 97}
    \item Terminal is in the top left tucked way in a corner.  Use the ladders to get to the highest level.
    \item Use this Terminal to query HSU and Color Key location
    \item Door on the left goes to 93 -- Security Scan (No Alarm)
    \item Door on the back goes to 97 -- Security Scan (No Alarm)
    \item Door on the right goes to 94 and leads to 95 -- \textbf{Requires Color Key}
\end{itemize}

\paragraph{ZONE\_093 - Room One West Sec Door}
\begin{itemize}
    \item {\color{Red}No Passage to other zones.}
    \item \gtfoterminal{Zone 93B on South Wall}% is in \texttt{ZONE\_093B} on the south wall of the room
    \item This zone will have a double \gtfoenemyscout{}
    \item Zone Letters from RIGHT to LEFT are \texttt{A - B - C}
    \item Zone 93E is at the North end of Zone 93C
\end{itemize}

\paragraph{ZONE\_094 - Room One East Sec Door (\alarm{Class 4})}
\begin{itemize}
    \item {\color{Blue}Passage to Zone 95 and Extreme Bulkhead (Zone 223)}
    \item Alarm Scan is: Single Red; 4 small red; 1 large red?
    \item This zone will have a single \gtfoenemyscout{}
    \item \textbf{EXTREME} Bulkhead Door is in Zone 94A (passage to Zone 224, 225, and 226)
    \item \gtfoterminal{Zone 94B} - near Zone 95 Security Door.
    \item Security Door to \texttt{ZONE\_095} is in Zone 94B on the East wall.  It is a normal security scan.
    \item \gtfobhhub{Zone 94B} is in a small corner of the south east side of the room.
\end{itemize}

\paragraph{ZONE\_095 (\securityscan{})}
\begin{itemize}
    \item {\color{Blue}Passage to Zone 96, Zone 98, Zone 99}
    \item This zone has chargers
    \item This zone has two \gtfoenemyscout{}
    \item Security Door to Zone 96 is in Zone 95A
    \item \gtfoterminal{Zone 95A} - near Zone 96 Security Door
\end{itemize}

\paragraph{ZONE\_096 (\emoji{police-car-light}\emoji{speaker-high-volume} Error Alarm! - Big Chargers)}
\begin{itemize}
    \item You have 3 mins until the first spawn shows up
    \item You will see two Big Chargers in your face every 30-45 seconds if you stand at the security door.
    \item \gtfoterminal{Zone 96E - to the East}
\end{itemize}

\paragraph{ZONE\_097 - Zone 92's North Sec Door}
\begin{itemize}
    \item The Security Door is on the North wall of Zone 92B
    \item This zone will have a \textbf{double} \gtfoenemyscout{}
    \item \gtfoterminal{Zone 97D} -- Up the entrance ramp to the immediate left.
    \item Zone Letters from LEFT to RIGHT are \texttt{D - B - C - E}; where E is downstairs from C.
\end{itemize}

\paragraph{ZONE\_098 (\erroralarm{}) -- Duplicate of Zone 96}
\begin{itemize}
    \item \gtfoterminal{Zone 98E - North Wall}
    \item HSU is likely in Zone 98E
    \item Completing the "DNA Sample" Scan will stop the alarm.
\end{itemize}

\paragraph{ZONE\_099 (\emoji{police-car-light} Class 4 Cluster Alarm)}
\begin{itemize}
    \item {\color{Blue}Passage to Overload Bulkhead (Zone 452)}
    \item This zone will contain a \gtfobhkey{}
    \item Security Door is on the South wall of Zone 95 up a ladder.
    \item This zone will have a single \gtfoenemyscout{}.
    \item \gtfoterminal{Zone 99B - East Wall}
\end{itemize}

\paragraph{ZONE\_223 - Extreme Bulkhead}
\begin{itemize}
    \item \emoji{warning} \textbf{The ENTIRE EXTREME IS INFECTION FOG!}
    \item All three Power Cells can be found in Zone 223.  Each is located in a different place.
\end{itemize}

\paragraph{ZONE\_224 (Bloody Door)}
\begin{itemize}
    \item Has one to two \gtfoenemyscout{}
    \item \gtfoterminal{Zone 224D} Under the stairs
    \item \gtfogenerator{Zone 224F} East wall next to blue tarp; Enter from E
\end{itemize}

\paragraph{ZONE\_225 (Bloody Door)}
\begin{itemize}
    \item Has one to two \gtfoenemyscout{}
    \item \gtfoterminal{WHERE?}
    \item \gtfogenerator{WHERE?} -- Required for Extreme Objective
\end{itemize}

\paragraph{ZONE\_226 (Bloody Door)}
\begin{itemize}
    \item Has one to two \gtfoenemyscout{}
    \item \gtfoterminal{WHERE?}
    \item \gtfogenerator{226F} -- Required for Extreme Objective
\end{itemize}

\paragraph{ZONE\_452 - Overload Bulkhead (No Alarm)}
\begin{itemize}
    \item The Bulkhead Hub for Overload is in Zone 99B
    \item This zone is completely dark, and features CHARGERS
    \item Zone 452A - Single \gtfoenemyscout{}
    \item There is a Mom in Zone 452A
    \item Terminal is in Zone 452B (around the corner from the hole in the wall in Zone 452A
    \item Use the aforementioned Terminal to "LIST REACTOR" and then "QUERY REACTOR\_..." it. (Zone 455)
    \item Zone 452D - Single \gtfoenemyscout{} + Chargers
    \item Zone 452F - Single \gtfoenemyscout{} + Chargers
    \item Zone 453 Security Door is on the East wall of Zone 452H
    \item Zone 456 Security Door is on the West wall of Zone 452A; Requires reactor to be online
\end{itemize}

\paragraph{ZONE\_453}
\begin{itemize}
    \item Terminal is in Zone 453B on East wall
    \item Zone 454 Security Door is on the East wall of Zone 453C
\end{itemize}

\paragraph{ZONE\_454 (No Alarm)}
\begin{itemize}
    \item Terminal is just through the Security Door to the left (North)
    \item Zone 454A - Single Charger \gtfoenemyscout{}
    \item Zone 455 Security Door is on the East side of the bridge in Zone 454A
\end{itemize}

\paragraph{ZONE\_455 - The Reactor (No Alarm)}
\begin{itemize}
    \item Terminal is on the East wall across from the center of the room
    \item Reactor Terminal is in the middle of the room
    \item Reactor is 7 waves!  Fight for 1m20s; 30s to enter code
    \item The last wave has Big Chargers in it; This wave is really hard.
    \item Round about wave 3 is when the Hybrids start showing up
\end{itemize}

\paragraph{ZONE\_456 - The Last Bulkhead Key}
\begin{itemize}
    \item Zone 456A - Single \gtfoenemyscout{} with no other enemies in the room
\end{itemize}
